---
title: "sample"
author: "Andrea"
date: "2/21/2023"
output: html_document
---


# Load these libraries
```{r}
suppressMessages(library(dplyr))
library(purrr)
library(tidyr)
library(utHelpR)
library(here)
library(DT)
set.seed(4561)
```


#Here we are using the **utHelp** package with the **get_data_from_sql_file** function
review the sql to see that it is pulling the right term, and right data elements needed for the sample
```{r, echo = FALSE}
students <- utHelpR::get_data_from_sql_file(file_name="current_students.sql",
                                               dsn="edify",
                                               context="project")
```

#Here we are determining sample sizes based on the groups (primary_level_class_id, college_id, age_band). Sampling 40% of each group (I need 3000 students, and my current students are 4740 - that is 40%).  Because it is 40%, we are excluding groups smaller than 2 (filter) because they will pull zero sample (2*.40 = .8). And selecting sample (samp).
```{r}
sample_students_1 <- students %>%
  group_by(primary_level_class_id, college_id, age_band) %>% 
  nest() %>%            
  ungroup() %>% 
  mutate(population_size = map_int(data, nrow)) %>%
  filter(population_size >= 2) %>% 
  mutate(sample_size = as.integer(.4*population_size)) %>% 
  mutate(samp = map2(data, sample_size, sample_n)) %>% 
  select(-data) %>%
  unnest(samp) 
```

```{r}
write.table(sample_students_1, here("sensitive/sample_innov.csv"),
          row.names = FALSE, col.names = TRUE, na = "",
          quote = FALSE, sep = ",", append = TRUE)
```

